---
title: "SNA methods draft"
author: "nic"
date: "2/7/2020"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
select<- dplyr::select
```

## Study site and data collection

We included females > 12 years and males > 15 years, as the former represented a move to reproductive maturity(?) and an end of adolescence. 200 subject-years. Subjects ranged 12 - 57 yo. 26.5 +/-  11.6 y, mean sd. Observations 1 - 8 years, 2010 - 2017. Age calculated at mid year.

```{r total subj, eval=FALSE}
library(tidyverse)
select<- dplyr::select

load("data/sna dataframe - weighted measures, individual sna measure for each year, network sex, & behavior.Rdata", verbose = TRUE)

all_sna_measure_df_w %>%
  distinct(chimp_id, sex, year) %>%
  group_by(sex) %>%
  tally()

all_sna_measure_df_w %>%
  distinct(chimp_id, year) %>%
  nrow()

all_sna_measure_df_w %>%
  summarise(max = max(age_mid_year), min = min(age_mid_year), mean = mean(age_mid_year), sd = sd(age_mid_year))

all_sna_measure_df_w %>%
  distinct(chimp_id, year) %>%
  count(chimp_id) %>%
  summarise(max_obs = max(n), min_obs = min(n))



```

## Data processing

#### Obs per year

1. Overall, we only included individuals that were either observed as a focal >= 100 hours per year, or observed as a focal for > 50 hrs AND present in social parties for at least 100 hours of focal observation.

```{r filter sub-years: low time as focal, eval = FALSE}
#load("data/total focal and possible focal per year (2009-2010 separate).Rdata", verbose = T)
load("data/total focal and possible focal per year.Rdata", verbose = T)

lo_focal <- total_poss_focal %>%
  mutate(focal_hours = n/4) %>% #scan every 15 minutes
  filter(focal_hours < 100) %>%
  rename(focal_n = n) %>%
  select(year, ID1, focal_n, focal_hours, short_presence) %>%
  arrange(year, ID1)
  
lo_focal

nrow(lo_focal) #92, 112 chimp-years w lo focal observations, i.e. < 100 hrs... (a lot!!!)

# many in 2009, 2011 & 2012
lo_focal %>%
  count(year)

```

```{r filter subj-years: time in party}
# Time in party
load("data/focal party scans formatted.Rdata", verbose = T)
source("functions/functions - data preparation.R")

total_party_member <- foc_part %>%
  count(ID2, year) %>%
  add_individ_attr(ID1 = "ID2") %>%
  add_age(dyad = F) %>%
  filter_age(dyad = F) %>%
  mark_short_time_pres_individ() %>%
  mutate(party_hours = n/4) %>%
  rename(party_n = n) %>%
  select(year, ID1, party_n, party_hours, short_presence) %>% arrange(year, ID1)
total_party_member #number of focal scans individaul was in party

#These are chimp-years to remove, lo focal hours and and lo party hours
lo_foc_lo_party <- lo_focal %>%
  left_join(.,total_party_member, by = c("year", "ID1", "short_presence")) %>%
  mutate(party_hours = replace_na(party_hours, 0)) %>% # for GS 2011
  filter(focal_hours < 50 & party_hours < 100) #everyone else will be between 50 and 100 hrs focaled and > 100 hrs in party
lo_foc_lo_party # 8 w 4 of these are removed for short presence, 11 pre 09-10 merge

lo_foc_lo_party %<>%
  filter(short_presence != 1)

#save(lo_foc_lo_party, file = "data/subject years to remove for low observations (focal and party membership).Rdata")
#apply in ghosts function - data preparation

#which lo focals are saved from exclusion bc of time in party?
lo_foc_hi_party <- lo_focal %>%
  left_join(total_party_member, by = c("year", "ID1", "short_presence")) %>%
  filter(party_hours >= 100)

nrow(lo_foc_hi_party) #84, 101

lo_focal %>% anti_join(lo_foc_lo_party) %>% anti_join(lo_foc_hi_party)
#should just be those w short pres

```


2. Focal animal sampling began in Aug 2009. But low avg observations per individuals, so we collated data from 2009 with 2010. 
```{r justify fold 2009 into 2010, eval=FALSE}
load("data/total focal and possible focal per year (2009-2010 separate).Rdata", verbose = T)

total_poss_focal %>%
  group_by(year) %>%
  summarise(mean = mean(n), sd = sd(n), spread_relative = sd/mean, min = min(n), max = max(n))

load("data/total focal and possible focal per year.Rdata", verbose = T)

total_poss_focal %>%
  group_by(year) %>%
  summarise(mean = mean(n), sd = sd(n), spread_relative = sd/mean, min = min(n), max = max(n))


```

Side exploration of obs time and integration:
bc low obs, see that gmgmd indices in 2009 are oddly high (prox are somewhat higher) and several sna measures are deviant. For example, in `annual_avg_sna` can see that deg is much lower and bt much higher in 2009 than other years.

```{r 2009 as outlier among social measures, eval=FALSE}
load("data/average social measures for exploration (with 2009 unweighted).Rdata", verbose = T)
#load("data/average social measures for exploration (sna weighted and 09-10 merged).Rdata", verbose = T)

#indices
annual_avg_gmgmd_mixed #2009 hi
annual_avg_gmgmd_sep # and is hi for both M and F

#sna measures
annual_sna_avg %>%
  filter(behavior == "prox")
```

Time as focal always correlates with network integration, no matter range of time obs...

```{r corr time observed and }
library(ggcorrplot)
load("data/sna dataframe - individual sna measure for each year, network sex, & behavior.Rdata", verbose = TRUE)

mat <- all_sna_measure_df %>%
  left_join(.,total_focal, by = c("chimp_id" = "ID1","year")) %>%
  mutate(hours_focal = n/4, hours_focal_hi = ifelse(n/4 > 500, n/4, NA)) %>%
  select(-n) %>%
  left_join(., total_party_member, by = c("chimp_id" = "ID2", "year")) %>%
  mutate(hours_party_member = n/4, hours_party_member_hi = ifelse(n/4 > 500, n/4, NA)) %>%
  select(-n) %>%
  select(ec,bt,deg, trans, hours_focal, hours_party_member, hours_focal_hi, hours_party_member_hi) 
mat
mat %>%
  cor(.,  method = "spearman", use = "pairwise.complete.obs")
mat %>%
  cor_pmat() %>%
  round(., 2)

#seems like observation time is always correlated with network integration...
```


3. We also excluded any individuals that were not present in the community for at least 6 months. Excluded 11 subject years for this.

```{r who was not present in community > 6 mo in given year?}
#load("data/total focal and possible focal per year (2009-2010 separate).Rdata", verbose = T)
load("data/total focal and possible focal per year.Rdata", verbose = T)
load("data/counts - gm and prox counts before removing short pres individs.Rdata", verbose = T)
source("functions/functions - data preparation.R")

shortpres_focal <- total_poss_focal %>% # is same as marked short time pres for gm and prox data directly
  filter(short_presence == 1) %>%
  select(year, ID1, sex) %>%
  arrange(year, ID1)

shortpres_focal

shortpres_focal %>%
 count(sex)
#none in 2009, start in 2011

#no overlap between low observation removals and short presence removals
nrow(shortpres_focal) #11
nrow(lo_foc_lo_party) #4
full_join(lo_foc_lo_party, shortpres_focal) %>% nrow() #15, no overlap

```

4. Each network member was observed as a focal subject for an annual average +/- sd of hours.
An average of X network members per year were never observed as a focal.

```{r average obs time}

```

We calculated annual affiliation indices gmgmd, prox, and gm, time associating during focal obs relative to time subjects seen in same party while one was a focal (as in machanda et al 2013 IJP). Analyzed measures of affiliation independently - as they appear to have diff functions or patterns among diff sex dyads (e.g. Machanda et al 2013)
Undirected (gmgmd prox) and directed (gm) annual networks with mixed and same sex dyads (9 networks) in R igraph
Calculated network centrality measures bt ec deg and local trans, with deg in and out for directed grooming
All measures weighted according to the aff index between individs
Calc sig using 1000 node permutations for attributes of chimp id, age, and sex

? changes in network sizes - and or changes in community size - year 2 year

------ graveyard

```{r avg obs in 2009}
load("data/total focal and possible focal per year (2009-2010 separate).Rdata", verbose = T)

total_focal %>%
  group_by(year) %>%
  summarise( mean = mean(n), sd = sd(n), spread_relative = sd/mean, max = max(n), min = min(n))

total_poss_focal %>%
  group_by(year) %>%
  summarise( mean = mean(n), sd = sd(n), spread_relative = sd/mean, max = max(n), min = min(n))

#spread in n 2010 is large
total_poss_focal %>%
  filter(year == 2013) %>%
  arrange(desc(n))


## removed for time pres
rm_gm <- total_gm_gmdx %>%
  mark_short_time_pres() %>%
  filter(short_presence_ID1 == 1) %>%
  distinct(year, ID1) %>%
  arrange(year, ID1)

rm_5 <- total_5mx %>%
  mark_short_time_pres() %>%
  filter(short_presence_ID1 == 1) %>%
  distinct(year, ID1) %>%
  arrange(year, ID1)

cbind(sp_focal, rm_gm, rm_5) 


