---
title: "SNA methods draft"
author: "nic"
date: "2/7/2020"
output: html_document
---

## Study site and data collection

We included females > 12 years and males > 15 years, as the former represented a move to reproductive maturity(?) and an end of adolescence. X unique subject-years

```{r setup, include=FALSE}
load("data/sna dataframe - individual sna measure for each year, network sex, & behavior.Rdata", verbose = TRUE)

all_sna_measure_df %>%
  distinct(chimp_id, sex, year) %>%
  group_by(sex) %>%
  tally()


```

## Data processing

Focal animal sampling began in Aug 2009. However, as few animals were focaled in this year, we excluded these initial data as we expect they did not result in a representative social networks.

```{r individuals focaled in 2009}
load("data/counts - dyadic focal party and total focal.Rdata", verbose = T)

total_focal %>%
  group_by(year) %>%
  summarise( mean = mean(n), sd = sd(n))

```

We excluded network members who were present in the community for < 6 months of a given observation year. 

```{r who was not present in community > 6 mo in given year?}
load("data/counts - gm and prox counts before removing short pres individs.Rdata", verbose = T)
load("functions/functions - data preparation.Rdata", verbose = T)

total_gm_gmdx %>%
  mark_short_time_pres() %>%
  filter(short_presence_ID1 == 1) %>%
  distinct(ID1, year, dls_ID1, immig_date_ID1, weeks_pres_ID1)

total_gm_gmdx %>%
  mark_short_time_pres() %>% 
  filter(weeks_pres_ID1 < 52) %>%
  distinct(ID1, year, dls_ID1, immig_date_ID1, weeks_pres_ID1, short_presence_ID1) %>%
  arrange(year, short_presence_ID1)

total_5mx %>%
  mark_short_time_pres() %>%
  filter(short_presence_ID1 == 1) %>%
  distinct(ID1, year, dls_ID1, immig_date_ID1, weeks_pres_ID1)


```

Each network member was observed as a focal subject for an annual average +/- sd of hours.
An average of X network members per year were never observed as a focal.

```{r average obs time}

```

We calculated affiliation
